\medskip
\subsection{Artificial Intelligence from Global Perspective}
\url{https://mitsloan.mit.edu/ideas-made-to-matter/new-report-details-growing-global-interest-artificial-intelligence}, a report from 2018, shows that interest in AI from a global level has been increasing rapidly in the past few decades.\\
Presently in 2021, the interest is still growing. Even more so when there are so many new technologies emerging that will require the power of AI to solve. Research focusing on AI has drastically increased. AI is applied to many aspect of our lives and work such as engineering, society, medications, and so on. So, it's crucial that everyone, interested in developing AI or not, knows the fundamental of AI as it will have a critical role in our daily lives in the near future.

\subsection{Artificial Intelligence in Thailand}
\url{https://thaiembdc.org/2021/04/28/ai-and-robotics-growing-rapidly-in-thailand/} \\ suggests the trend of AI in Thailand and shows related statistics.\\
Similar to the global level, AI in Thailand is also growing at a rapid rate. We have the foundation ready for AI and automation industry. So, it's predicted that AI trend will grow in the future to support the country's economic, industry, and increase productivity.

\subsection{Existing Learning Source about AI}
\paragraph{University Curriculum about AI in Thailand}
In some universities, AI education exists in the form of an extra credit that students can choose to apply.\\
\url{https://www.admissionpremium.com/content/5909} shows the courses that major in AI engineering. There are only 2 public universities that currently have the AI engineering department which are King Mongkut's Institute of Technology Ladkrabang and Chulalongkorn University. Others are private universities which are considerably more costly than private universities.

\subsection{Online AI courses and Educational Programming Games}
There are a lot of online courses available for learning AI such as Udemy, coursera, edX, and so on. There are also educational games for learning coding fundamentals such as Code Combat, Minecraft: Hour of Code, Scratch, and lots more. But when it comes to educational games for AI, there are quite a few. Some are focused on competitive AI coding which is not friendly for beginner. \\
\url{https://studio.code.org/s/oceans/} This is an interesting example of games that teach the concept of AI. It has a great design and concepts, cute gameplay, and good for learning the basic of AI and image recognition. 
\vspace{-5mm}
\paragraph{Educational Games and Programming} ~\\
\url{https://www.researchgate.net/publication/305084679_Learning_Programming_through_Games_and_Contests_Overview_Characterisation_and_Discussion}
reviews some good platform to learn programming. \\[5cm]
\url{https://www.researchgate.net/publication/267034149_Educational_Games_for_Teaching_Computer_Programming} discusses about important characteristics of educational coding games. Additionally, it goes over some educational programming games and their uniqueness as well. \\
\url{https://files.eric.ed.gov/fulltext/EJ1233506.pdf} explores the effectiveness of using games to teach programming concepts and problem solving skills. The game used in this research is PROSOLVE. \\
These researches provide us with great resource of how our game should be in order to be effective for the players to learn while playing. It also proves that games are useful for learning programming concepts as well.