\medskip
\subsection{Miro}
\url{https://miro.com/app/dashboard/} is an online whiteboard and visual collaboration platform. This is what we use to organize our ideas, storyboard, and role as it is a good tool for working and brainstorming online. 
\subsection{Notion}
\url{https://www.notion.so/} is an application that provides components such as notes and databases. Providing lots of tools and blocks, notion can help users their own systems for note taking and data management. We use it to store our information and meeting notes. 
\subsection{Microsoft Planner}
\url{https://tasks.office.com/mail.kmutt.ac.th/en-US/Home/Planner/} is a project management tool that will help users manage their tasks and projects. We use it to distribute tasks and our project timeline. 
\subsection{Fire Alpaca and Clip Studio Paint}
\url{https://firealpaca.com/} and \url{https://www.clipstudio.net/en/} are tools for creating computer graphics. We use these to create pixel art for maps and sprites in our games.
\subsection{Garage Band}
\url{https://www.apple.com/mac/garageband/} is a line of digital audio workstations for macOS, iPadOS, and iOS devices that allows users to create music or podcasts. We use this tool to create soundtracks and background music for our games.
\subsection{GitHub}
\url{https://github.com/} is a provider of Internet hosting for software development and version control using Git. We use it to share our code, work collaboratively online, and manage the version control for our game.
\subsection{Godot Engine}
\url{https://godotengine.org/} is a cross-platform, free and open-source game engine released under the MIT license. We use this tool to develop our game because it is well documented, beginner friendly, and appropriate for our game.